An Axiomatic Basis for Computer Programming: Review

### 2017-02-16 hoare/paper.tex
Desribe rule of consequence

>>>>

And we could notice that predicate $P_1$ is stronger that predicate $P$. By
``stronger'' we mean that $P_1 \implies P$, or informally, if predicate $P_1$
holds for some values, predicate $P$ will holds either. But opposite is not true
(in our case $x = 0$ doesn't hold in $P_1$).

So we could make preconditions stronger, program will still be correct.

With postcondition predicates, on the contrary, we couldn't make it
stronger.

Because if we don't change program $Q$, it will produce range of
results, which satisfy weaker predicate.

This range is superset of set which satisfy stronger predicate.

So $Q$ will produce values which don't satisfy postcondition - program will be
incorrect according to stronger predicate.

But we could make postcondition weaker, program will still be correct.

This is actually Rule of Consequence stated in Hoare paper.

But lets return to our example.

% We prove correctness of statement on conditions $P_!$ and $Q$. But we should
% consider

In case when $x = 0$ (or $P \wedge \neg B$) equation takes the form:
$$ bx + c = 0 \text{, and } x = \frac{-c}{b}$$

Yet again this remains true when $C \equiv b \neq 0$ is true, so this statement
is correct according to precondition $P \wedge \neg B \wedge C$ and
postcondition $R$.

As you can see, we try discharge proof by cases, and then, using Condition
Rule (or Rule of Iteration), prove correctness of their combination.

In case when $b = 0$ or $\neg C$, equation takes the form:
$$ c = 0$$

Either $c = 0$ and equation holds for all $x \in \mathbb{R}$, or $c \neq 0$ and
equation
